PANCHANGE_descriptives

### 2020-11-11 PANCHANGE_exclusion_descriptives.Rmd
Changed aesthetics for the little/much better prepan retro scatterplots

much_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse",
                      sep=" "),
        subtitle = paste("n", dim(much_worse_gad_scatter)[1]))

little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
                      sep=" "),
        subtitle = paste("n", dim(little_worse_gad_scatter)[1]))

much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse and a little worse",
                      sep=" "),
        subtitle = paste("n", dim(much_little_worse_gad_scatter)[1]))

much_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse",
                      sep=" "),
        subtitle = paste("n", dim(much_worse_phq_scatter)[1]))

little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little worse",
                      sep=" "),
        subtitle = paste("n", dim(little_worse_phq_scatter)[1]))

much_little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse and a little worse",
                      sep=" "),
        subtitle = paste("n", dim(much_little_worse_phq_scatter)[1]))

@@

little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little better",
                      sep=" "),
        subtitle = paste("n", dim(little_better_gad_scatter)[1]))

much_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better",
                      sep=" "),
        subtitle = paste("n", dim(much_better_gad_scatter)[1]))

much_little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") + 
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better and a little better",
                      sep=" "),
        subtitle = paste("n", dim(much_little_better_gad_scatter)[1]))

little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little better",
                      sep=" "),
        subtitle = paste("n", dim(little_better_phq_scatter)[1]))

much_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") +
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better",
                      sep=" "),
        subtitle = paste("n", dim(much_better_phq_scatter)[1]))

much_little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "blue") +
  stat_smooth(method = "lm") + 
  geom_jitter(w = 0.4, h = 0.4) +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better and a little better",
                      sep=" "),
        subtitle = paste("n", dim(much_little_better_phq_scatter)[1]))

>>>>

much_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse",
                      sep=" "),
        subtitle = paste("n", dim(much_worse_gad_scatter)[1]))

little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little worse",
                      sep=" "),
        subtitle = paste("n", dim(little_worse_gad_scatter)[1]))

much_little_worse_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +  
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much worse and a little worse",
                      sep=" "),
        subtitle = paste("n", dim(much_little_worse_gad_scatter)[1]))

much_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse",
                      sep=" "),
        subtitle = paste("n", dim(much_worse_phq_scatter)[1]))

little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little worse",
                      sep=" "),
        subtitle = paste("n", dim(little_worse_phq_scatter)[1]))

much_little_worse_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much worse and a little worse",
                      sep=" "),
        subtitle = paste("n", dim(much_little_worse_phq_scatter)[1]))

@@

little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "blue", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting a little better",
                      sep=" "),
        subtitle = paste("n", dim(little_better_gad_scatter)[1]))

much_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better",
                      sep=" "),
        subtitle = paste("n", dim(much_better_gad_scatter)[1]))

much_little_better_gad_scatter %>% ggplot(aes(x = gad.sum_score_prepan, y = gad.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") + 
   labs(title = paste("Relationship between prepandemic and retrospective GAD scores\nfor participants reporting much better and a little better",
                      sep=" "),
        subtitle = paste("n", dim(much_little_better_gad_scatter)[1]))

little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting a little better",
                      sep=" "),
        subtitle = paste("n", dim(little_better_phq_scatter)[1]))

much_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") +
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better",
                      sep=" "),
        subtitle = paste("n", dim(much_better_phq_scatter)[1]))

much_little_better_phq_scatter %>% ggplot(aes(x = phq.sum_score_prepan, y = phq.sum_score_retro)) +
  geom_point(colour = "grey") +
  geom_jitter(w = 0.4, h = 0.4, colour = "grey") +
  geom_smooth(method = "lm", colour = "navy", fill = "red") + 
   labs(title = paste("Relationship between prepandemic and retrospective PHQ scores\nfor participants reporting much better and a little better",
                      sep=" "),
        subtitle = paste("n", dim(much_little_better_phq_scatter)[1]))
